---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# EarthquakeAnalysis

<!-- badges: start -->
<!-- badges: end -->

The goal of EarthquakeAnalysis is to complete the MSDR Capstone project on Coursera.

This capstone project will be centered around a dataset obtained from the U.S. National Oceanographic and Atmospheric Administration (NOAA) on significant earthquakes around the world. 


## Installation

You can install the development version of EarthquakeAnalysis like so:

```{r installation, eval=FALSE}
library(devtools)
install_github("BFavetto/EarthquakeAnalysis")
library(EarthquakeAnalysis)
```

## Example

This is a basic example which shows you how to plot a map with recent earthquakes in Italy:

```{r example, eval=FALSE}
library(dplyr)
library(ggplot2)

# load the dataset
data("NOAAdata")

NOAAdata %>% eq_clean_data() %>%
  eq_location_clean() %>%
  filter(Country %in% "ITALY" &
               lubridate::year(Date) >= 2000) %>%
  eq_map(annot_col = "Date")
```


